Spatio-temporal estimates of HIV risk group proportions for adolescent girls and young women across 13 priority countries in sub-Saharan Africa

### 2023-01-25 src/docs_paper/paper.Rmd
Prospective final conclusion update

<!-- TODO: Follow up with Clemens r.e. FSW group name: -->
<!-- There are a couple of options: female sex workers, young women from key populations (and clarify in the text that you mean sex work), AGYW who sell sex. Many people who do this work all the time use "FSW" so likely fine, but there's also a move away from defining someone by their job making "who sell sex" possibly the preferred option. -->

@@

To calculate HIV prevalence by risk group, we disaggregated the district-age specific prevalence estimates from Naomi estimates to risk groups using odds ratios for the relative odds of having HIV between risk groups, calculated from a logistic regression of country-age specific household survey HIV bio-marker data.
<!-- TODO: Be more specific about the data source here. -->
Prevalence disaggregation was on the logit scale to ensure that HIV prevalence in each risk group remained in the range 0\% to 100\%.
The number of PLHIV was calculated by multiplying HIV prevalence by risk group population size.

@@

<!-- How does this vary by country / region?  Maybe worth calling out result for West Africa vs. East Africa vs. Southern Africa here to highlight the difference. Also how does this compare with other estimates? And what does Oli think about this? I recognize that comparison is not straightforward because age group difference! -->

@@

<!-- Are we able to add an analysis of the number who are prioritized for the 'standard' and 'enhanced' prevention packages in the Global Strategy? That gets a lot of emphasis in the Introduction, so would be nice to report about here. -->

@@

We estimated the proportion of AGYW who fall into different risk groups at a district level in 13 sub-Saharan African countries.
Our estimates support consideration of differentiated prevention programming according to geographic locations and risk behaviour, as outlined in the Global AIDS Strategy.
Systematic differences in risk by age groups, and variation within and between countries, explained the large majority of variation in risk group proportions.
Changes over time were negligible in the overall variation in risk group proportions.
The proportion of 15-19 year olds who are sexually active, and among women aged 20-29 years, norms around cohabitation especially varied across districts and countries.
This variation underscores the need for these granular data to implement HIV prevention options aligned to local norms and risk behaviours.
<!-- Some type of comment about how novel this would be if implemented -->

@@

<!-- Paragraph about AGFS e.g. our results are consistent with age at first sex findings [@nguyen2022trends]. -->

@@

We estimated the proportion of AGYW aged 15-19, 20-24 and 25-29 years in four sexual risk categories at a district-level in 13 priority countries and analyzed the number of infections that could be reached by prioritisation based upon location, age and behaviour.
Though subject to limitations, these estimates provide data that national HIV programmes can use to set targets and implement differentiated HIV prevention strategies as outlined in the Global AIDS Strategy.
Successfully implementing this approach would result in more efficientlt reaching a greater number of those at risk of infection.

<!-- TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->

>>>>

<!-- Possible TODO: Follow up with Clemens r.e. FSW group name: -->
<!-- There are a couple of options: female sex workers, young women from key populations (and clarify in the text that you mean sex work), AGYW who sell sex. Many people who do this work all the time use "FSW" so likely fine, but there's also a move away from defining someone by their job making "who sell sex" possibly the preferred option. -->

@@

To calculate HIV prevalence by risk group, we disaggregated the district-age specific prevalence estimates from Naomi estimates to risk groups using odds ratios for the relative odds of having HIV between risk groups, calculated from a logistic regression of country-age specific household survey HIV bio-marker data.
<!-- Possible TODO: Be more specific about the data source here. -->
Prevalence disaggregation was on the logit scale to ensure that HIV prevalence in each risk group remained in the range 0\% to 100\%.
The number of PLHIV was calculated by multiplying HIV prevalence by risk group population size.

@@

<!-- Possible TODO: How does this vary by country / region?  Maybe worth calling out result for West Africa vs. East Africa vs. Southern Africa here to highlight the difference. Also how does this compare with other estimates? And what does Oli think about this? I recognize that comparison is not straightforward because age group difference! -->

@@

<!-- Possible TODO: Are we able to add an analysis of the number who are prioritized for the 'standard' and 'enhanced' prevention packages in the Global Strategy? That gets a lot of emphasis in the Introduction, so would be nice to report about here. -->

@@

We estimated the proportion of AGYW who fall into different risk groups at a district level in 13 sub-Saharan African countries.
Our estimates support consideration of differentiated prevention programming according to geographic locations and risk behaviour, as outlined in the Global AIDS Strategy.
Systematic differences in risk by age groups, and variation within and between countries, explained the large majority of variation in risk group proportions.
Changes over time were negligible in the overall variation in risk group proportions.
The proportion of 15-19 year olds who are sexually active, and among women aged 20-29 years, norms around cohabitation especially varied across districts and countries.
This variation underscores the need for these granular data to implement HIV prevention options aligned to local norms and risk behaviours.
<!-- Possible TODO: Some type of comment about how novel this would be if implemented -->

@@

<!-- Possible paragraph about AGFS e.g. our results are consistent with age at first sex findings [@nguyen2022trends]. -->

@@

We estimated the proportion of AGYW aged 15-19, 20-24 and 25-29 years in four sexual risk groups at a district-level in 13 priority countries and analyzed the number of infections that could be reached by prioritisation based upon location, age and behaviour.
Though subject to limitations, these estimates provide data that national HIV programmes can use to set targets and implement differentiated HIV prevention strategies as outlined in the Global AIDS Strategy.
Successfully implementing this approach would result in more efficiently reaching a greater number of those at risk of infection.

Among AGYW, there was systematic variation by age group in risk group proportions, primary attributable to sexual debut typically occurring during the ages 15-24.
There was also large amounts of spatial variation, particularly between those who reported one cohabiting partner versus non-regular or multiple partners.
Risk group proportions did not change substantially over time, indicating that norms relating to sexual behaviour are relatively static.
These findings underscore the importance of providing effective HIV prevention options tailored to the needs of particular age groups, as well as local sexual norms.

<!-- Possible TODO: Add "... and highlight the need to consider country-specific contexts." once there is more discussion of this in main text. -->
